Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting

### 2025-04-30 products/manuscript/Manuscript.qmd
update

# Goodness-of-fit & diagnostics
library(generalhoslem)      # Hosmer–Lemeshow tests
library(ResourceSelection)  # Additional GOF tests
library(rms)                # Regression modeling strategies
library(car)                # Companion to applied regression

```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table1Baseline.png")

```

@@

**Figure 1: Distribution of Total Malaria Episodes by IPTp Treatment Arm**
```{r,echo=FALSE, message=FALSE, warning=FALSE}}
knitr::include_graphics("Images/Figure1.DistribTotal Malaria.png")

```

@@

**Table 2: Outcome Measures and Malaria Exposure Variables Stratified by IPTp Regimen**
```{r}
knitr::include_graphics("Images/Table2.Outcome Measures Malaria .png")

```

@@

```{r,echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table4Interaction.png")

```

@@

**Table 4: Adjusted Odds Ratios for Adverse Birth Outcomes Among Young Pregnant Women (<25 Years)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/AdjustedRatio.png")

```

@@

**Figure 4: Predicted Probability of Adverse Outcome by Gravidity (Age < 25)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Figure 3. Predicted Probability.png")

```

@@

**Table 5:  Discriminative Performance (AUC) of Machine Learning Models Predicting Adverse Birth Outcomes Under Different IPTp Regimens**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table6.Discriminative Performance (AUC) of ML Models.png")

```

@@

**Figure 5 : Comparative Discriminative Performance of ML Models for Predicting Adverse Birth Outcomes**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Figure 4.Comparative Discriminative Performance of ML .png")

```

>>>>

# Goodness-of-fit & diagnostics
library(generalhoslem)      # Hosmer–Lemeshow tests
library(ResourceSelection)  # Additional GOF tests
library(rms)                # Regression modeling strategies
library(car)                # Companion to applied regression
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table1Baseline.png")
```

@@

**Figure 1: Distribution of Total Malaria Episodes by IPTp Treatment Arm**
```{r,echo=FALSE, message=FALSE, warning=FALSE}}
knitr::include_graphics("Images/Figure1.DistribTotal Malaria.png")
```

@@

**Table 2: Outcome Measures and Malaria Exposure Variables Stratified by IPTp Regimen**
```{r}
knitr::include_graphics("Images/Table2.Outcome Measures Malaria .png")
```

@@

```{r,echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table4Interaction.png")
```

@@

**Table 4: Adjusted Odds Ratios for Adverse Birth Outcomes Among Young Pregnant Women (<25 Years)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/AdjustedRatio.png")
```

@@

**Figure 4: Predicted Probability of Adverse Outcome by Gravidity (Age < 25)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Figure 3. Predicted Probability.png")
```

@@

**Table 5:  Discriminative Performance (AUC) of Machine Learning Models Predicting Adverse Birth Outcomes Under Different IPTp Regimens**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table6.Discriminative Performance (AUC) of ML Models.png")
```

@@

**Figure 5 : Comparative Discriminative Performance of ML Models for Predicting Adverse Birth Outcomes**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Figure 4.Comparative Discriminative Performance of ML .png")
```
